The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add slides and figs for corollaries

Let $f_1, f_2$ continuous on $[0, 1]$. Then
$$
f_1(t) \leq f_2(t) \;\forall\, t
$$
$$
\implies \phi_P^\infty(f_1) \leq \phi_P^\infty(f_2)
$$

In words: the platform gets a larger slice when

  * the firms are substitutes to each other
  * the platform has intrinsic value

@@

>>>>

::: {.fragment fragment-index=1}
The platform gets a larger slice when
:::
::: {.fragment fragment-index=2}
  1. the firms are substitutes to each other
:::
::: {.fragment fragment-index=3}
  2. the platform has intrinsic value
:::
::: {.fragment fragment-index=4}
  3. the fringe firms have no outside option
:::

@@

::: {.fragment fragment-index=1}
   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/draw_graph.mp4" />
:::
::: {.fragment fragment-index=2}
   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/complements.mp4" />
:::
::: {.fragment fragment-index=3}
   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/intrinsic_value.mp4" />
:::
::: {.fragment fragment-index=4}
   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/outside_option.mp4" />
:::
